Cosmic web correlations with the shape, spin and peculiar velocties of dark matter halos

### 2013-11-06 paper/main.tex
new figure in paper
first take on the interweb alignment

In this \documentname we use the Bolshoi volume. This is a simulation
that follows the non-linear evolution of a dark matter density field
on cosmological scales. The volume is a cubic box with 250\hMpc on a
side, the matter density field is sampled with $2048^3$ particles. The
cosmological parameters in the simulation correspond to the results
inferred from WMAP5 data, which are also consistent with the more
recent results of WMAP9. These parameters are $\Omega_m=0.27$,
$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
matter density, cosmological constant, normalization of the power
spectrum, the slope in the spectrum of the primordial matter
fluctuation and the dimensionless Hubble constant. With this
conditions the mass of each dark matter particle in the simulation
corresponds to $m_p=1.4\times 10^{8}$\hMsun.

@@

\subsection{Interweb Alignment}
... We compute the pair-wise allignment between the eigenvectors in
the two web finders.

... We also compute the alignment between the eigenvectors in cells
occupied by dark matter halos. This will be a key element in the
interpretation of the results for halo-based allignments in the next
sections: shape, angular momentum and peculiar velocities.

...

\begin{figure}
\includegraphics[width=0.40\textwidth]{web.pdf}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).} 
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.48\textwidth]{ax_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{ax_V_cut.pdf}
\includegraphics[width=0.48\textwidth]{J_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{J_V_cut.pdf}
\includegraphics[width=0.48\textwidth]{v_T_cut.pdf}
\includegraphics[width=0.48\textwidth]{v_V_cut.pdf}
\caption{The alignment is always taken with respect to the first eigenvector.}
\end{figure*}

\section{Discussion}
\label{sec:discussion}

>>>>

In this \documentname we use the Bolshoi simulation that follows the
non-linear evolution of a dark matter density field on cosmological
scales. The volume is a cubic box with 250\hMpc on a side, the matter
density field is sampled with $2048^3$ particles. The  
cosmological parameters in the simulation correspond to the results
inferred from WMAP5 data, which are also consistent with the more
recent results of WMAP9. These parameters are $\Omega_m=0.27$,
$\Omega_{\Lambda} =0.73$, $\sigma_8=0.82$, $n_s=0.95$ and $h=0.70$ for the
matter density, cosmological constant, normalization of the power
spectrum, the slope in the spectrum of the primordial matter
fluctuation and the dimensionless Hubble constant. With this
conditions the mass of each dark matter particle in the simulation
corresponds to $m_p=1.4\times 10^{8}$\hMsun.

@@

\subsection{Interweb Alignment}

In the first place we wish to directly compare the results of the two
algorithms. For the two algorithms we have the information for the
eigenvectors and the eigenvalues on exactly the same positions defined
by the grids. This allows us tocompute the pair-wise allignment
between the eigenvectors in the two web finders.

We are mainly interested in the alginment of the web with
the halos. Therefore we restrict our analysis to the grid cells that are
occupied by halos. If we had decided to perform this kind of analysis
on all the grid cells, the statistics would be dominated by the void
regions, because the dominate in number the fraction of cells in the
simuation.

Figure \ref{fig:interweb} shows the results of the inter-web alignment
as a function of halo mass. It clearly stands out that the
eigenvectors are aligned for low mass halos but are close perpendicular to
each other at the location of the most massive halos. There is a
transition scale around $(10^{11.5}-10^{12.5})$\hMsun depending on the
grid resolution. The coarse grid $(256^3)$shows the transition at higher masses
than the fine grid $(512^3)$.

For both resolutions, the halos more massiven than $10^{13}$\hMsun are
locate in regions where the fastest momentum-weighted collapse
direction (defined by the V-web) is perpendicular to the direction
where the tidal compression is the highest.

The fact that this trend is less evident at low resolution and low
masses, hints that the flip is actually related to the overdensity
values, i.e. to the degree of non-linearity, in the corresponding
spatial scales.

\begin{figure}
\includegraphics[width=0.40\textwidth]{web.pdf}
\caption{Median of the interweb alignment for the two grid
  resolutions as a function of the dark matter mass corresponding to
  the halos where the measurement was made. The error bars indicate
  the lower and upper quartiles (Figure in color in the web version).
\label{fig:interweb}} 
\end{figure}

@@

\begin{figure*}
\includegraphics[width=0.90\textwidth,angle=90]{all_cuts.pdf}
\caption{The alignment is always taken with respect to the first eigenvector.}
\end{figure*}
\section{Discussion}
\label{sec:discussion}
